Experiment 5: Replication Analysis

### 2024-11-03 group-b/E2-analysis-replication.Rmd

```{r, eval = F}
ggplot(fixed.view.data %>% filter(subject_id == '5f7c9ab9b52d920f0aa8ab4e'))+
  geom_point(aes(x = x, y = y, color = view_quadrant))+
  geom_point(data = fixed.view.data %>% filter(subject_id == '5f7c9ab9b52d920f0aa8ab4e' & central_fix),
             aes(x = x, y = y ), color = "black")+
  scale_y_reverse()+
  theme_bw()+
  theme(legend.position = "none")

@@

```{r E2-gaze-fig-free, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.", eval =FALSE, out.width="50%", fig.align="center"}
fig<-ggplot(free.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
  geom_col(position=position_dodge(), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
  scale_fill_brewer(palette="Set1",)+
  theme_classic(base_size = 25)+
  coord_cartesian(ylim = c(0, 0.4))+
  labs(x = "Quadrant", y = "Mean proportion of looks")+
  theme(legend.position = "none")
fig
```
```{r saving plot, eval=FALSE}
saveRDS(fig, "output/ETfig.rds")
ggsave("output/ETfig.png", plot = fig, width  = 8.5, height = 5.5)
```

@@

ggplot(view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
  geom_col(position=position_dodge(), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
  facet_wrap(~condition)+
  scale_fill_brewer(palette="Set1",)+
  theme_classic()+
  labs(x = "Quadrant", y = "Mean proportion of looks")+
  theme(legend.position = "none")

@@

```{r E2-gaze-fig-fixed, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.", eval = F, out.width="50%", fig.align="center"}
fig.fixed<-ggplot(fixed.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
  geom_col(position=position_dodge(), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
  scale_fill_brewer(palette="Set1",)+
  theme_classic()+
  labs(x = "Quadrant", y = "Mean proportion of looks")+
  theme(legend.position = "none")
fig.fixed
```

@@

acc_fig<-ggplot(acc.summary.condition.data %>% 
                 mutate(relation = factor(relation, levels = c("intra", "inter"))), 
                        aes(x=relation, color=condition, y=M, ymax=M+SE, ymin=M-SE, group=condition))+
  geom_point(size=5)+
  geom_line()+
  geom_errorbar(width=0.2)+
  scale_color_manual(values=c("orange2","royalblue4"))+
  coord_cartesian(ylim=c(0.3,0.8)) +
  labs(x="Statement Type", y="Accuracy", color=NULL)+
  theme_classic()
```

@@

rt_fig<-ggplot(rt.summary.condition.data %>% 
                 mutate(relation = factor(relation, levels = c("intra", "inter"))), 
               aes(x=relation, color=condition, y=M, ymax=M+SE, ymin=M-SE, group=condition))+
  geom_point(size=5)+
  geom_line()+
  geom_errorbar(width=0.2)+
  scale_color_manual(values=c("orange2","royalblue4"))+
  labs(x="Statement Type", y="Response Time (ms)", color=NULL)+
  theme_classic()
```

>>>>

```{r, eval = F}
ggplot(fixed.view.data %>% filter(subject_id == '5f7c9ab9b52d920f0aa8ab4e'))+
  geom_point(aes(x = x, y = y, color = view_quadrant))+
  geom_point(data = fixed.view.data %>% filter(subject_id == '5f7c9ab9b52d920f0aa8ab4e' & central_fix),
             aes(x = x, y = y ), color = "black")+
  scale_y_reverse()+
  theme_bw()+
  theme(legend.position = "none") + theme(
    panel.grid.minor = element_blank(),
    axis.title = element_text(size=14),     
    axis.text = element_text(size=14)
  )

@@

```{r E2-gaze-fig-free, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.", eval =FALSE, out.width="50%", fig.align="center"}
fig<-ggplot(free.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
  geom_col(position=position_dodge(), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
  scale_fill_brewer(palette="Set1",)+
  theme_classic(base_size = 25)+
  coord_cartesian(ylim = c(0, 0.4))+
  labs(x = "Quadrant", y = "Mean proportion of looks")+
  theme(legend.position = "none") + theme(
    panel.grid.minor = element_blank(),
    axis.title = element_text(size=14),      # Axis titles
    axis.text = element_text(size=14),       # Axis labels
    legend.title = element_text(size=14),    # Legend title
    legend.text = element_text(size=14)      # Legend text
  )

fig
```
```{r saving plot, eval=FALSE}
saveRDS(fig, "output/ETfig.rds")
ggsave("output/ETfig.png", plot = fig, width  = 8.5, height = 5.5)
```

@@

ggplot(view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
  geom_col(position=position_dodge(), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
  facet_wrap(~condition)+
  scale_fill_brewer(palette="Set1",)+
  theme_classic()+
  labs(x = "Quadrant", y = "Mean proportion of looks")+
  theme(legend.position = "none") +     theme(
    panel.grid.minor = element_blank(),
    axis.title = element_text(size=14),  
    axis.text = element_text(size=14)
  )

@@

```{r E2-gaze-fig-fixed, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.", eval = F, out.width="50%", fig.align="center"}
fig.fixed<-ggplot(fixed.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
  geom_col(position=position_dodge(), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
  scale_fill_brewer(palette="Set1",)+
  theme_classic()+
  labs(x = "Quadrant", y = "Mean proportion of looks")+
  theme(legend.position = "none")    theme(
    panel.grid.minor = element_blank(),
    axis.title = element_text(size=14), 
    axis.text = element_text(size=14)
  )

fig.fixed
```

@@

acc_fig<-ggplot(acc.summary.condition.data %>% 
                 mutate(relation = factor(relation, levels = c("intra", "inter"))), 
                        aes(x=relation, color=condition, y=M, ymax=M+SE, ymin=M-SE, group=condition))+
  geom_point(size=5)+
  geom_line()+
  geom_errorbar(width=0.2)+
  scale_color_manual(values=c("orange2","royalblue4"))+
  coord_cartesian(ylim=c(0.3,0.8)) +
  labs(x="Statement Type", y="Accuracy", color=NULL)+
  theme_classic() + theme(
    panel.grid.minor = element_blank(),
    axis.title = element_text(size=14),      # Axis titles
    axis.text = element_text(size=14),       # Axis labels
    legend.title = element_text(size=14),    # Legend title
    legend.text = element_text(size=14)      # Legend text
  )

@@

rt_fig<-ggplot(rt.summary.condition.data %>% 
                 mutate(relation = factor(relation, levels = c("intra", "inter"))), 
               aes(x=relation, color=condition, y=M, ymax=M+SE, ymin=M-SE, group=condition))+
  geom_point(size=5)+
  geom_line()+
  geom_errorbar(width=0.2)+
  scale_color_manual(values=c("orange2","royalblue4"))+
  labs(x="Statement Type", y="Response Time (ms)", color=NULL)+
  theme_classic() +     theme(
    panel.grid.minor = element_blank(),
    axis.title = element_text(size=14),      # Axis titles
    axis.text = element_text(size=14)
  )

### 2024-11-03 group-d/E4-analysis-comparison-to-original.Rmd

```{r E4-mouse-moves-fig-web-and-orig, fig.cap = "Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online."}

@@

```{r E4-proportion-fix-by-window-both, fig.cap = "Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online. Error bars reflect bootstrapped 95% CIs over subject means"}

ggplot(eyetracking.window.summary.by.subj.both)+
  stat_summary(aes(x=time.window, color=condition, y = mean_prop, shape = study), 
               geom = 'point', fun = 'mean', size = 3)+
 stat_summary(aes(x=as.numeric(time.window), y = mean_prop, linetype = study, group=paste(condition, study) ),
             geom = 'line', fun = 'mean', alpha = 0.5, color = "grey")+
  stat_summary(aes(x=as.numeric(time.window), y = mean_prop, color = condition, group = paste(condition , study)), 
                geom = 'errorbar', fun.data = 'mean_cl_boot', width = 0.05)+
  #facet_wrap(~time.window)+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values = c(1,16))+
  scale_linetype_manual(values = c("dashed","solid"))+
  coord_cartesian(ylim = c(0,.8))+
  theme_classic()+
  labs(y = "Proportion of fixations", x = NULL)
```
```{r, eval  = F}
orig.data.time.window.1 <- eyetracking.window1.summary.by.trial.orig %>% 
  filter(condition != "filler") %>% 
  mutate(condition = fct_drop(condition))
contrasts(orig.data.time.window.1$condition) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))

>>>>

```{r E4-mouse-moves-fig-web-and-orig, fig.cap = "Proportion of first mouse movements by location and verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online.", out.width="65%", fig.align="center"}

@@

```{r E4-proportion-fix-by-window-both, fig.cap = "Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online. Error bars reflect bootstrapped 95% CIs over subject means", , out.width="75%", fig.align="center"}

ggplot(eyetracking.window.summary.by.subj.both)+
  stat_summary(aes(x=time.window, color=condition, y = mean_prop, shape = study), 
               geom = 'point', fun = 'mean', size = 3)+
 stat_summary(aes(x=as.numeric(time.window), y = mean_prop, linetype = study, group=paste(condition, study) ),
             geom = 'line', fun = 'mean', alpha = 0.5, color = "grey")+
  stat_summary(aes(x=as.numeric(time.window), y = mean_prop, color = condition, group = paste(condition , study)), 
                geom = 'errorbar', fun.data = 'mean_cl_boot', width = 0.05)+
  #facet_wrap(~time.window)+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values = c(1,16))+
  scale_linetype_manual(values = c("dashed","solid"))+
  coord_cartesian(ylim = c(0,.8))+
  theme_classic()+
  labs(y = "Proportion of fixations", x = NULL) +     theme(
    panel.grid.minor = element_blank(),
    axis.title = element_text(size=14),      # Axis titles
    axis.text = element_text(size=14),       # Axis labels
    legend.title = element_text(size=14),    # Legend title
    legend.text = element_text(size=14)      # Legend text
  )

```{r, eval  = F}
orig.data.time.window.1 <- eyetracking.window1.summary.by.trial.orig %>% 
  filter(condition != "filler") %>% 
  mutate(condition = fct_drop(condition))
contrasts(orig.data.time.window.1$condition) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))

### 2024-11-03 group-e/E5-analysis-replication.Rmd

plot.A<-ggplot(summary.gaze.view[summary.gaze.view$task=="Attractiveness",], aes(x=time.window, y=prop.in.target))+
  geom_point(color="red") + 
  geom_line(data=fit.A.dat, aes(x=x, y=y), color="red", lwd=1.25, linetype = "solid") + 
  scale_x_reverse() + theme_classic() + 
  labs(x="Time until decision (ms)", y="Proportion of gaze in target", color="Task", fill="Task") + ylim(.4, 1)

plot.R<-ggplot(summary.gaze.view[summary.gaze.view$task=="Roundness",], aes(x=time.window, y=prop.in.target))+
  geom_point(color="turquoise4") + 
  geom_line(data=fit.A.dat, aes(x=x, y=y), color="red", lwd=1.25, linetype = "dashed") + 
  geom_line(data=fit.R.dat, aes(x=x, y=y), color="turquoise4", lwd=1.25, linetype = "solid") + 
  scale_x_reverse() + theme_classic() + 
  labs(x="Time until decision (ms)", y="Proportion of gaze in target", color="Task", fill="Task") + ylim(.4, 1)

>>>>

plot.A<-ggplot(summary.gaze.view[summary.gaze.view$task=="Attractiveness",], aes(x=time.window, y=prop.in.target))+
  geom_point(color="red") + 
  geom_line(data=fit.A.dat, aes(x=x, y=y), color="red", lwd=1.25, linetype = "solid") + 
  scale_x_reverse() + theme_classic() + 
  labs(x="Time until decision (ms)", y="Proportion of gaze in target", color="Task", fill="Task") + ylim(.4, 1) +     theme(
    panel.grid.minor = element_blank(),
    axis.title = element_text(size=14),      # Axis titles
    axis.text = element_text(size=14),       # Axis labels
    legend.title = element_text(size=14),    # Legend title
    legend.text = element_text(size=14)      # Legend text
  )

plot.R<-ggplot(summary.gaze.view[summary.gaze.view$task=="Roundness",], aes(x=time.window, y=prop.in.target))+
  geom_point(color="turquoise4") + 
  geom_line(data=fit.A.dat, aes(x=x, y=y), color="red", lwd=1.25, linetype = "dashed") + 
  geom_line(data=fit.R.dat, aes(x=x, y=y), color="turquoise4", lwd=1.25, linetype = "solid") + 
  scale_x_reverse() + theme_classic() + 
  labs(x="Time until decision (ms)", y="Proportion of gaze in target", color="Task", fill="Task") + ylim(.4, 1) +     theme(
    panel.grid.minor = element_blank(),
    axis.title = element_text(size=14),      # Axis titles
    axis.text = element_text(size=14),       # Axis labels
    legend.title = element_text(size=14),    # Legend title
    legend.text = element_text(size=14)      # Legend text
  )
